---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sclr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/khvorov45/sclr.svg?branch=master)](https://travis-ci.org/khvorov45/sclr)
[![codecov](https://codecov.io/gh/khvorov45/sclr/branch/master/graph/badge.svg)](https://codecov.io/gh/khvorov45/sclr)
<!-- badges: end -->

The goal of sclr is to fit the scaled logit model from Dunning (2006) using the
maximum likelihood method.

## Installation

The package is not yet on [CRAN](https://CRAN.R-project.org). You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("khvorov45/sclr")
```

## Model

For log likelihood, scores and second derivatives see `vignette("Math", "sclr")`.
Documentation of the main fitting function `?sclr` has details on how the model is fit.

## Example

Usage is similar to other model fitting functions like `lm`.

```{r example}
library(sclr)
fit <- sclr(status ~ logHI, sclr_one_titre_data)
summary(fit)
```

For more details see `vignette("Usage", "sclr")`.

## References

Dunning AJ (2006). “A model for immunological correlates of protection.” Statistics in Medicine, 25(9), 1485-1497. doi: 10.1002/sim.2282.

